Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Fixing errors

The evaluation metric follow the metric used in ActivityNet Challenge to regard classification and temporal activity localization as retrieval probelm and evaluate the mAP.
For temporal localization, a prediction is masrked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.

>>>>

The evaluation metric follows the one used in ActivityNet Challenge with regard to classification and temporal activity localization as a retrieval problem, evaluating the mAP.
For temporal localization, a prediction is marked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
